Exception Handling Bug Hazards in Android

### 2016-04-20 SPRINGER_JOURNAL/msr_journal.tex
formating issues

 The NullPointerException was mainly signaled inside the application code (50\%) and the Android platform (31.5\%),
 although we could also find the NullPointerException being signaled by third-party libraries (16.3\%).
Regarding reusable code (e.g., libraries and frameworks), there is no consensus whether it is a good or a bad practice to
explicitly throw a NullPointerException. Some prefer to encapsulate such an exception in
an instance of IllegalArgumentException, while others~\cite{bloch2008effective} argue that the
NullPointerException makes the cause of the problem explicit and hence
can be signaled by an API expecting a non-null argument.The high prevalence of NullPointerException is aligned with the
findings of other
research~\cite{kim2013predicting,fraser20131600,csallner2004jcrasher,kechagia2014}.
For instance, Kechagia and Spinellis showed that the NullPointerException was the
most reported exception in the crash reports sent to BugSense~\footnote{https://www.bugsense.com/} (a bug report
management service for Android applications)~\cite{kechagia2014}.
Other research on robustness testing~\cite{maji2012empirical,csallner2004jcrasher} shows that most of the automatically
detected bugs were due to NullPointerException and exceptions
implicitly signaled by the Java
environment due to programming mistakes or resource limitations
 (as the ones found in our study).

@@

%\subsubsection{Can the exception types reveal bug hazards?}
\noindent\emph{RQ 1.2 Can the exception types reveal bug hazards?}
%\subsection{Exploring the Information Embedded on Exception Types}
%\subsection{The Exception Types and What They can Tell us? }

@@

%TABLE 5 WAS HERE

@@

%\textcolor{red}
The survey comprises multiple choice or Likert-scale questions and open-ended questions. The multiple choice questions are intermixed with open-ended questions to further elicit the developer's opinions. Moreover, the survey also contains Likert-scale questions to force participants to make a choice. Overall, the survey includes 13 open-ended questions, 5 Likert-scale questions and 10 multiple choice questions. The respondents could complete the survey in about 15 minutes.

%\textcolor{red}
We used grounded theory coding to iterate through the open-ended survey responses. The grounded theory coding used in this study consists of two phases: (1) initial coding entails a close reading of the data and (2) later we used focused coding ~\cite{charmaz2006} to pinpoint and develop the most salient themes ~\cite{charmaz2006} in the analyzed data. Answers to different questions in the survey were coded separately. For all open-ended questions in the survey, coding was done by two researchers until saturation was reached. Disagreements were discussed and resolved as part of the coding, thus, we are unable to report level of agreement. In all cases, the first author was one of the two coders, and one of the other authors coded the data as well in close collaboration with the first author until saturation was reached. The first author then went through the remaining responses to assign codes to responses.

>>>>

 The NullPointerException was mainly signaled inside the application code (50\%) and the Android platform (31.5\%),
 although we could also find the NullPointerException being signaled by third-party libraries (16.3\%).
Regarding reusable code (e.g., libraries and frameworks), there is no consensus whether it is a good or a bad practice to
explicitly throw a NullPointerException. Some prefer to encapsulate such an exception in
an instance of IllegalArgumentException, while others~\cite{bloch2008effective} argue that the
NullPointerException makes the cause of the problem explicit and hence
can be signaled by an API expecting a non-null argument.

The high prevalence of NullPointerException is aligned with the
findings of other
research~\cite{kim2013predicting,fraser20131600,csallner2004jcrasher,kechagia2014}.
For instance, Kechagia and Spinellis showed that the NullPointerException was the
most reported exception in the crash reports sent to BugSense~\footnote{https://www.bugsense.com/} (a bug report
management service for Android applications)~\cite{kechagia2014}.
Other research on robustness testing~\cite{maji2012empirical,csallner2004jcrasher} shows that most of the automatically
detected bugs were due to NullPointerException and exceptions
implicitly signaled by the Java
environment due to programming mistakes or resource limitations
 (as the ones found in our study).

@@

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
%\subsubsection{Can the exception types reveal bug hazards?}
\noindent\emph{RQ 1.2 Can the exception types reveal bug hazards?}
%\subsection{Exploring the Information Embedded on Exception Types}
%\subsection{The Exception Types and What They can Tell us? }

@@

%TABLE 5 WAS HERE
\bigskip

@@

The survey comprises multiple choice or Likert-scale questions and open-ended questions. The multiple choice questions are intermixed with open-ended questions to further elicit the developer's opinions. Moreover, the survey also contains Likert-scale questions to force participants to make a choice. Overall, the survey includes 13 open-ended questions, 5 Likert-scale questions and 10 multiple choice questions. The respondents could complete the survey in about 15 minutes.

We used grounded theory coding to iterate through the open-ended survey responses. The grounded theory coding used in this study consists of two phases: (1) initial coding entails a close reading of the data and (2) later we used focused coding ~\cite{charmaz2006} to pinpoint and develop the most salient themes ~\cite{charmaz2006} in the analyzed data. Answers to different questions in the survey were coded separately. For all open-ended questions in the survey, coding was done by two researchers until saturation was reached. Disagreements were discussed and resolved as part of the coding, thus, we are unable to report level of agreement. In all cases, the first author was one of the two coders, and one of the other authors coded the data as well in close collaboration with the first author until saturation was reached. The first author then went through the remaining responses to assign codes to responses.
